### 2023-03-11 chapter0/chapter0.tex
Added stem for function paragraph and discussion of MoRFs and fuzzy complexes

In contrast, IDRs have no fixed spatial relationship between their atoms and are sometimes described as ``conformational ensembles,'' \textit{i.e.} a collection of related structures.

>>>>

The structural diversity of IDRs is directly related to their functional plasticity.

Although the previous discussion has presented of disorder and structure as distinct phenomona , disorder is a spectrum
MorFs
folding on binding
fuzzy complexes
